Norwegian citizen science data exploration

### 2018-02-15 paper.Rmd
Improve legend readability

long_dataset <- c(min(ao_data_subset$decimallongitude) %/% 1 , max(ao_data_subset$decimallongitude) %/% 1 + 1)
lat_dataset <- c(min(ao_data_subset$decimallatitude) %/% 1 , max(ao_data_subset$decimallatitude) %/% 1 + 1)
```

@@

ggplot(ao_data_subset) + annotation_map(world_map, fill="gray50", colour="gray50") +
    geom_point(aes(x=decimallongitude, y=decimallatitude, color=species), alpha=0.5, size=cellsize/gridsizeinkm, shape=15) +
    theme(panel.background = element_rect(fill="aliceblue"), legend.position = "right") +
    coord_map(projection = "gnomonic", orientation=c(60, 16, -5),
              xlim=long_dataset,  # limits on longitude
              ylim=lat_dataset) + # limits on latitude
    xlab("Longitude") +
    ylab("Latitude")

@@

```{r rasterize, message=FALSE, echo=FALSE}
  gridsizeinkm <- 50
  cellsize <- (lat_dataset[2] - lat_dataset[1]) * gridsizeinkm * .0016
  ao_data_subset <- rasterize(ao_data_subset, gridsizeinkm)
```

@@

ggplot(ao_data_subset) + 
    annotation_map(world_map, fill="gray50", colour="gray50") +
    geom_point(aes(x=long_rounded, y=lat_rounded, color=species), alpha=0.3, size = .5 * cellsize) +
    theme(panel.background = element_rect(fill="aliceblue"), legend.position = "right") +
    coord_map(projection = "gnomonic", orientation=c(60, 16, -5),
              xlim=long_dataset,  # limits on longitude
              ylim=lat_dataset) + # limits on latitude
   xlab("Longitude") + ylab("Latitude")

>>>>

long_dataset <- c(min(ao_data_subset$decimallongitude) %/% 1 , max(ao_data_subset$decimallongitude) %/% 1 + 1)
lat_dataset <- c(min(ao_data_subset$decimallatitude) %/% 1 , max(ao_data_subset$decimallatitude) %/% 1 + 1)

gridsizeinkm <- 50
cellsize <- (lat_dataset[2] - lat_dataset[1]) * gridsizeinkm * .0016

@@

ggplot(ao_data_subset) + annotation_map(world_map, fill="gray50", colour="gray50") +
    geom_point(aes(x=decimallongitude, y=decimallatitude, color=species), alpha=0.5, size=cellsize/gridsizeinkm, shape=15) +
    theme(panel.background = element_rect(fill="aliceblue"), legend.position = "right") +
    guides(color = guide_legend(override.aes = list(size=4))) +
    coord_map(projection = "gnomonic", orientation=c(60, 16, -5),
              xlim=long_dataset,  # limits on longitude
              ylim=lat_dataset) + # limits on latitude
    xlab("Longitude") +
    ylab("Latitude")

@@

```{r rasterize, message=FALSE, echo=FALSE}
  ao_data_subset <- rasterize(ao_data_subset, gridsizeinkm)
```

@@

ggplot(ao_data_subset) + 
    annotation_map(world_map, fill="gray50", colour="gray50") +
    geom_point(aes(x=long_rounded, y=lat_rounded, color=species), alpha=0.3, size = .5 * cellsize) +
    theme(panel.background = element_rect(fill="aliceblue"), legend.position = "right") +
    guides(color = guide_legend(override.aes = list(size=4))) +
    coord_map(projection = "gnomonic", orientation=c(60, 16, -5),
              xlim=long_dataset,  # limits on longitude
              ylim=lat_dataset) + # limits on latitude
   xlab("Longitude") + ylab("Latitude")
